Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-27 docs/papers/roofline_model/gocean_roofline.tex
roofline: add data and plots for investigation of daxpy kernels
roofline: update text and labelling of daxpy roofline

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2} we plot the
results obtained from the DAXPY component of the STREAM2 benchmark on
both of the CPUs examined here. The plateaux in bandwidth for L2, L3
and main memory are clear but that for L1 is considerably noisier. The
final values we have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}.

\begin{figure}
\includegraphics{stream2_desktop}
\includegraphics{stream2_archer}
\caption{Results from running the STREAM2 benchmark on the E5-1620
  (top) and E5-2697 (bottom) CPUs.}
\label{FIG_stream2}
\end{figure}

>>>>

Interpreting the results of the STREAM benchmark in order to get
bandwidth figures for all levels of the cache hierarchy is not
straightforward. We therefore used the STREAM2 benchmark which is
intended for this purpose. In Figure~\ref{FIG_stream2} we plot the
results obtained from the DAXPY component of the STREAM2 benchmark on
the E5-2697 CPU (using v.~14 {\bf (check this)} of the Intel
compiler. The plateaux in bandwidth for L2, L3 and main memory are
clear but that for L1 is considerably noisier. The final values we
have used in the roofline plots are given in
Table~\ref{TAB_stream_linpack}.

\begin{figure}
\includegraphics[width=120mm]{stream2_archer}
\caption{Results from running the STREAM2 benchmark on the E5-2697
  CPUs. Error bars indicate the maximum and minimum values obtained
  from 200 repeats of each case.  size. }
\label{FIG_stream2}
\end{figure}

 The equivalent results for the E5-1620
CPU are shown in Figure~\ref{FIG_daxpy_bw}. This plot has the same
shape as that for the E5-2697 but is shifted upwards indicating a
considerable increase in bandwidth accross all levels of the cache
hierarchy. {\bf need to check by re-running on Archer with 200 repeats
  and new min/max results}. In addition, the width of the plateau
corresponding to the L3 cache is narrower because of the smaller size
of this cache on the E5-1620.

\begin{figure}
\includegraphics[width=120mm]{daxpy_plot}
\caption{Bandwidth obtained on the E5-1620 CPU by the original and
  modified versions of the daxpy kernel from the STREAM2 benchmark.}
\label{FIG_daxpy_bw}
\end{figure}

\begin{figure}
\includegraphics[width=120mm]{roofline_daxpy}
\caption{Roofline plot of daxpy-based kernels on the E5-1620 CPU. Each
  cluster of bars represents a different kernel. Bars within a cluster
  are for problem sizes chosen to fit within the L3, L2 and L1 cache
  (arrays of 94,427, 8271 and 1533 elements, respectively). }
\label{FIG_daxpy_roofline}
\end{figure}
